Implications of afforestation policies for global markets

### 2024-02-26 paper.Rmd
Update paper.Rmd

@@

# Results
We first examined the impact of a scenario where the rate of deforestation globally was reduced to zero through the implementation of a uniform global tax rate on the conversion of forestland to agricultural land. A tax rate of roughly 70 percent was required to achieve this. With this policy in place, most regions of the world would see significant declines in the amount of agricultural land in 2030 relative to the baseline scenario where land conversion was not taxed. For the United States, agricultural land would be 2.1 percent less (Table 1). Larger decreases would happen in important regions such as Brazil (-9.7 percent), the rest of South America (-14.7 percent), Southeast Asia (-10.0 percent), and Sub-Saharah Africa (-4.8 percent).

Table 1 qo-Land
	                         ∆ (%)
Central America	                -16.9
East Asia	                -14.4
North Africa & the Middle East	-11.1
Southeast Asia	                -10.0
Russia	                         -9.8
Brazil	                         -9.7
Rest of South America	        -14.7
South Asia	                 -9.1
Canada	                         -8.1
Oceania	                         -7.5
European Union	                 -6.4
Sub-Saharan Africa	         -4.8
EUII	                         -3.3
China	                         -2.5
United States	                 -2.1
Japan	                         11.4

These reductions in the amount of agricultural land prompt changes in the quantity of agricultural goods produced for many regions. For example, East Asia and Southeast Asia see the largest declines in percentage terms in agricultural production with decreases of 5.9 percent and 2.8 percent, respectively (Table 2). Surprisingly, Brazil and the United States, despite the derease in available agricultural land compared to the baseline 2030 scenario, see increased agricultural output of 0.2 percent and 0.8 percent, respectively. This may be tied to the sharp declines in other regions prompting greater production for export.

Table 2 qo-Ag
			∆ (%)
East Asia		-5.9
Southeast Asia		-2.8
Central America		-2.7
South Asia		-2.1
Rest of South America	-1.6
North Africa & the Middle East	-1.2
Sub-Saharan Africa	-0.5
China			-0.1
Russia			0.1
Brazil			0.2
EUII			0.3
European Union		0.4
United States		0.8
Oceania			0.9
Canada			1.3
Japan			1.5

Table 3 qxw-Ag
				∆ (%)
				Agriculture
Japan				13.5
United States			5.0
Canada				2.6
Russia				2.4
Oceania				2.2
EUII				2.2
China				1.5
European Union			1.4
Brazil				1.4
Sub-Saharan Africa		0.0
North Africa & the Middle East	-2.3
Rest of South America		-3.8
Central America			-6.9
Southeast Asia			-7.3
South Asia			-11.0
East Asia			-19.8

>>>>

Then, we examined what it would take given the pressures of a still growing global population with the concomitant increasing appetite for foodstuffs to end, on net, the practice of deforestation globally. Results suggest that it would require a tax of roughly 70.3 percent to be assessed on the value of the converted land for the deforestation rate to fall globally to roughly zero. The economic impact of such a policy measure would not be limited to the cost of the tax, it would also change impact food production and global trade. For example, with this policy in place, most regions of the world would see significant declines in the amount of agricultural land in 2033 relative to the baseline scenario where land conversion was not taxed. For the United States, agricultural land would be 2.1 percent less (Table 1). Larger decreases would happen in other major agricultural production regions such as China (-2.5 percent), South Asia (-8.0 percent), Brazil (-8.5 percent), and Russia (-9.3 percent).

Table 1 qo-Land
				∆ (%)
East Asia			-14.6
Central America			-14.5
North Africa & the Middle East	-10.3
Russia				-9.3
Southeast Asia			-9.0
Brazil				-8.5
Rest of South America		-11.7
South Asia			-8.0
Canada				-7.9
West & Central Europe 		-6.2
Oceania				-5.9
Sub-Saharan Africa		-4.1
China				-2.5
United States			-2.2
Japan				17.5

These reductions in the amount of agricultural land prompt changes in the quantity of agricultural goods produced for many regions. For example, East Asia and Southeast Asia see the largest declines in percentage terms in agricultural production with decreases of 5.1 percent and 2.0 percent, respectively (Table 2). Surprisingly, Brazil and the United States, despite the derease in available agricultural land compared to the baseline 2033 scenario, see increased agricultural output of 0.2 percent and 0.6 percent, respectively. This may be tied to the sharp declines in other regions prompting greater production for export.

Table 2 qo-Ag
				∆ (%)
				Agriculture
East Asia			-5.1
Southeast Asia			-2.0
Central America			-2.0
South Asia			-1.1
North Africa & the Middle East	-0.9
Sub-Saharan Africa		-0.3
China				-0.1
Russia				0.1
Brazil				0.2
Rest of South America		-1.2
West & Central Europe 		0.4
United States			0.6
Oceania				0.7
Canada				1.3
Japan				1.4

Table 3 qxw-Ag
				∆ (%)
				Agriculture
East Asia			-5.1
Southeast Asia			-2.0
Central America			-2.0
South Asia			-1.1
North Africa & the Middle East	-0.9
Sub-Saharan Africa		-0.3
China				-0.1
Russia				0.1
Brazil				0.2
Rest of South America		-1.2
West & Central Europe 		0.4
United States			0.6
Oceania				0.7
Canada				1.3
Japan				1.4

@@
